---
title: "Replicating Figure 1a in Kolokotrones, 2010"
author:
  - Hannah Fung:
      email: hffung@stanford.edu
      institute: [Stanford]
      correspondence: true
  - Raeline Corryn Valbuena:
      email: raecv@stanford.edu
      institute: [Stanford]
      correspondence: true
  - Ronghao Zhou:
      email: ronghao@stanford.edu
      institute: [Stanford]
      correspondence: true
institute:
  - Stanford: Stanford University, Biosciences
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/nature.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  body mass, basal metabolic rate, replication
highlights: |
  Final project for Just Enough Software Engineering. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

<!-- The actual document text starts here: -->

# Introduction

This is a replication of figure 1a from [@kolokotrones2010] (Fig. \@ref(fig:fig1a)).

# Background

# Methods

# Results

```{r load}
library(readxl)
library(tidyverse)
library(Kolokotrones)
library(dplyr)
library(ggplot2)
```

```{r get-data}
# Path we need to use to access our data files when rendering this document
data <- read_excel(here::here("analysis/data/41586_2010_BFnature08920_MOESM90_ESM_elephant.xls"), skip = 6)
# general parsing of data column names and values
names(data) <- str_replace_all(names(data), c(" " = ".",
                                              "[(]" = "",
                                              "[)]" = ""))
data <- data[!is.na(data$Mass.g),]
# head(data)
```

```{r regressions}
# prepare additional columns for regressions
data <- data %>%
  mutate(log_Mass = log10(Mass.g),
         log_Mass2 = log_Mass^2, 
         log_BMR = log10(BMR.W))

# parse the data for values of interest 
drop_genera <- (c("Elephas", "Orcinus"))
sub_data <- subset_data(data, drop_genera)
drop_data <- anti_join(data, sub_data, by = "Genus")

# generate linear regression
lin_reg <- lm(log_BMR ~ log_Mass, sub_data)
# generate prediction of linear regression
pred_data_lin <- tibble(
  log_Mass = seq(from=0, to=max(data$log_Mass), length.out = 100)
) %>% mutate(log_BMR = stats::predict(lin_reg, newdata = .))

# generate quadratic regression
qua_reg <- lm(log_BMR ~ log_Mass+log_Mass2, sub_data)
# generate prediction of quadratic regression
pred_data_qua <- tibble(
  log_Mass = seq(from=0, to=max(data$log_Mass), length.out = 100),
  log_Mass2 = log_Mass^2
) %>% mutate(log_BMR = stats::predict(qua_reg, newdata = .))
```


```{r elephant_orca_data}
elephant_data <- data %>% filter(Genus == 'Elephas')
orca_data <- data %>% filter(Genus == 'Orcinus')
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r fig1a, fig.cap="Replication of figure 1a from [@kolokotrones2010]"}
# set colors equal to original publication
colors = c("Linear" = "red",
           "Quadratic" = "blue",
           "Elephant (not included in fit)" = "turquoise",
           "Orca (not included in fit)" = "sea green")
# generate figure 1a using ggplot2
ggplot(sub_data, aes(x=log_Mass, y=log_BMR)) + 
  geom_point(size = 0.5) +
  geom_line(data = pred_data_lin,
            aes(color = "Linear"),
            size = 1) +
  geom_line(data = pred_data_qua, 
            aes(color = "Quadratic"),
            size = 1) + 
  geom_point(data = elephant_data,
             aes(color = 'Elephant (not included in fit)'),
             shape = 15,
             size = 2) +
  geom_point(data = orca_data,
             aes(color = 'Orca (not included in fit)'),
             shape = 15,
             size = 2)+
  theme_minimal() +
  theme(legend.position=c(0.2, 0.8),
        legend.title = element_blank(),
        axis.line=element_line(colour="black"), 
        legend.background = element_rect(fill="white",
                                  size=0.5, linetype="solid", 
                                  color ="black")) +
  labs(x=expression("log"[10]*"[M (g)]"), 
     y=expression("log"[10]*"[B (W)]"), 
     title="Figure 1: Curvature in metabolic scaling.",
     color = "Legend") +
  scale_color_manual(values = colors)

```

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
