---
title: "Replicating Figure 1a in Kolokotrones, 2010"
author:
  - Hannah Fung:
      email: hffung@stanford.edu
      institute: [Stanford]
      correspondence: true
  - Raeline Corryn Valbuena:
      email: raecv@stanford.edu
      institute: [Stanford]
      correspondence: true
  - Ronghao Zhou:
      email: ronghao@stanford.edu
      institute: [Stanford]
      correspondence: true
institute:
  - Stanford: Stanford University, Biosciences
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/nature.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  body mass, basal metabolic rate, replication
highlights: |
  Final project for Just Enough Software Engineering. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

<!-- With the following code you can access and display values from the yml header above. -->

Keywords: `r rmarkdown::metadata$keywords`

Highlights: `r rmarkdown::metadata$highlights`

<!-- The following code chunk defines some general settings how code chunks should behave. -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

<!-- The actual document text starts here: -->

# Introduction

This is a replication of figure 1a from [@kolokotrones2010] (Fig. \@ref(fig:fig1a)).

# Background

# Methods

# Results

```{r load}
library(readxl)
library(tidyverse)
library(Kolokotrones)
library(dplyr)
library(ggplot2)
```

```{r get-data}
# Note the path that we need to use to access our data files when rendering this document
data <- read_excel(here::here("analysis/data/41586_2010_BFnature08920_MOESM90_ESM.xls"), skip = 6)
names(data) <- str_replace_all(names(data), c(" " = ".", "[(]" = "", "[)]" = ""))
data <- data[!is.na(data$Mass.g),]
# head(data)

```

```{r regressions}



# # linear regression
# lin_reg <- lm(log10(BMR.W) ~ log10(Mass.g), sub_data)
# 
# pred_data_lin <- tibble(
#   Mass.g = seq(from=min(data$Mass.g), to=max(data$Mass.g), length.out = 100)
# ) %>% 
#   mutate(BMR.W = 10^(stats::predict(lin_reg, newdata = .)))
# 
# # quadratic regression
# sub_data$Mass2 <- sub_data$Mass.g^2
# qua_reg <- lm(log10(BMR.W) ~ log10(Mass.g)^2 + log10(Mass.g), sub_data)
# 
# pred_data_qua <- tibble(
#   Mass.g = seq(from=min(data$Mass.g), to=max(data$Mass.g), length.out = 100)
# ) %>% 
#   mutate(BMR.W = 10^(stats::predict(qua_reg, newdata = .)))

# linear regression
data$log_Mass <- log10(data$Mass.g)
data$log_Mass2 <- data$log_Mass^2
data$log_BMR <- log10(data$BMR.W)

# parse the data for R 
drop_genera <- (c("Elephantulus", "Orcinus"))
sub_data <- subset_data(data, drop_genera)
drop_data <- anti_join(data, sub_data, by = "Genus")

lin_reg <- lm(log_BMR ~ log_Mass, sub_data)

pred_data_lin <- tibble(
  log_Mass = seq(from=0, to=max(data$log_Mass), length.out = 100)
) %>% 
  mutate(log_BMR = stats::predict(lin_reg, newdata = .))

# quadratic regression

qua_reg <- lm(log_BMR ~ log_Mass+log_Mass2, sub_data)

pred_data_qua <- tibble(
  log_Mass = seq(from=0, to=max(data$log_Mass), length.out = 100),
  log_Mass2 = log_Mass^2
) %>% 
  mutate(log_BMR = stats::predict(qua_reg, newdata = .))

Elephant_data <- data %>% filter(Genus.Species == 'Elephantulus myurus')
Orca_data <- data %>% filter(Genus == 'Orcinus')
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r fig1a, fig.cap="Replication of figure 1a from [@kolokotrones2010]"}

# ggplot(sub_data, aes(x=log10(Mass.g), y=log10(BMR.W))) + 
#   geom_point(size = 0.5) +
#   theme_minimal() +
#   theme(legend.position="left") +
#   # geom_point(drop_data, aes(x=log10(Mass.g), y=log10(BMR.W))) +
#   geom_line(data = pred_data_lin, # <- change the data
#             color = 'red',
#             size = 1.5) +
#   geom_line(data = pred_data_qua, # <- change the data
#             color = 'blue',
#             size = 1) + 
#   labs(x=expression("log"[10]*"[M (g)]"), 
#      y=expression("log"[10]*"[B (W)]"), 
#      title="Figure 1: Curvature in metabolic scaling.") +
#   scale_color_manual(name="", values=c("Linear"="red","Quadratic"="blue"))
 
ggplot(sub_data, aes(x=log_Mass, y=log_BMR)) + 
  geom_point(size = 0.5) +
  theme_minimal() +
  theme(legend.position="left", 
        axis.line=element_line(colour="black")) +
  geom_line(data = pred_data_lin, # <- change the data
            color = 'red',
            size = 1.5) +
  geom_line(data = pred_data_qua, # <- change the data
            color = 'blue',
            size = 1) + 
  labs(x=expression("log"[10]*"[M (g)]"), 
     y=expression("log"[10]*"[B (W)]"), 
     title="Figure 1: Curvature in metabolic scaling.") +
  # geom_point(Elephant_data, aes(x=log_Mass, y=log_BMR),shape='square') +
  scale_color_manual(name="", values=c("Linear"="red","Quadratic"="blue")) 


```

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break  -->

\newpage

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

::: {#refs}
:::

\newpage

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```
